\documentclass[conference]{IEEEtran}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}
\title{Comparison Among Automatic Exploration Tools for Android Applications}

\author{\IEEEauthorblockN{Michael Osorio-Riaño}
\IEEEauthorblockA{\textit{Department of Systems and Computing Engineering } \\
\textit{University of Los Andes}\\
Bogotá, Colombia\\
ms.osorio@uniandes.edu.co}
\textit{Advised by: Mario Linares-Vásquez}\\
\textit{m.linaresv@uniandes.edu.co}\\
\textit{Assistant Professor at University of Los Andes}
}

\maketitle

\input{content/abstract}\\

\begin{IEEEkeywords}
Android, Móvil, Pruebas, Exploración Automática,Ingeniería de Software empírica
\end{IEEEkeywords}

\input{content/introduction}

\input{content/relatedWork}

\input{content/objectives}

\input{content/study}


\input{content/results}

\input{content/conclusions}

\input{content/futureWork}

\begin{thebibliography}{00}
\bibitem{b1} Android monkey,

http://developer.android.com/guide/developing/tools/monkey.html.
\bibitem{b2}Android testing framework,

http://developer.android.com/guide/topics/testing/index.html.
\bibitem {b3} Amit Seal Ami, Md. Mehedi Hasan, Md. Rayhanur Rahman, and Kazi Sakib. 2018. Mobicomonkey: context testing of Android apps. In Proceedings of the 5th International Conference on Mobile Software Engineering and Systems (MOBILESoft '18). ACM, New York, NY, USA, 76-79.
\bibitem{b4} Young-Min Baek and Doo-Hwan Bae. 2016. Automated model-based Android GUI testing using multi-level GUI comparison criteria. In Proceedings of the 31st IEEE/ACM International Conference on Automated Software Engineering (ASE 2016). ACM, New York, NY, USA, 238-249.
\bibitem{b5} Ting Su, Guozhu Meng, Yuting Chen, Ke Wu, Weiming Yang, Yao Yao, Geguang Pu, Yang Liu, and Zhendong Su. 2017. Guided, stochastic model-based GUI testing of Android apps. In Proceedings of the 2017 11th Joint Meeting on Foundations of Software Engineering (ESEC/FSE 2017). ACM, New York, NY, USA, 245-256.
\bibitem{b6} Nariman Mirzaei, Joshua Garcia, Hamid Bagheri, Alireza Sadeghi, and Sam Malek. 2016. Reducing combinatorics in GUI testing of android applications. In Proceedings of the 38th International Conference on Software Engineering (ICSE '16). ACM, New York, NY, USA, 559-570.
\bibitem {b7} Y. Zhauniarovich, A. Philippov, O. Gadyatskaya, B. Crispo and F. Massacci, "Towards Black Box Testing of Android Apps," 2015 10th International Conference on Availability, Reliability and Security, Toulouse, 2015, pp. 501-510.
\end{thebibliography}


\end{document}